MSF_Groupwork-NBA_shotlog

### 2016-10-16 MSFGroupwork-NBAHotHand.Rmd
minor changes

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
knitr::opts_chunk$set(echo = TRUE)
```
##Report produced by: Justin Leiendecker, Alexander Romanenko, Artmeis Tomadaki-Balomenou, Zijun Wei, Reza Brianca Widodo  
##Date submitted: 16/10/2016

@@

The NULL Hypothesis: Teams playing at home is more likely to win then when playing away. 
The NULL Hypothesis: Analysis of means for home and away wins does not show any significant difference

###Methods
Steps to test the hypothesis are as follows:  
    1. Calculate a total number of games, which has been won by a home or away team
    2. Compare the total win numbers to identify whether home advantage is evident using means of the variables
    3. Extend the analysis to review of the home/away wins on a team level 
    4. Plot the team level data 
    5. Perform a t-test (p .05) to examine whether there is a difference in the means between teams winning at home and teams winning away
    6. Linear regression with Final margin as dependent variable and Location as independent variable to examine whether playing at home results predicts a higher final margin

The graph below shows descriptive statistics for home/away wins:

@@

###Findings
**Table 1**: Proportion of total games split by Location win factor

@@

The T-test used to verify the differences in the means seen in the plot reached significance, t(58) = -2.39, p = .02.

###Regression analysis

@@

The steps to calculate this measurement are as follows:  
    1. Calculating number of rest days between games for all teams
    3. Calculating ratios for effects of rest days on win/loss form home/away
    4. Perform a Chi-square test to examine whether there is a difference in the distributon for games won and games lost for the different restdays
    5. Calculating ratios for effects of rest days on win/loss form home/away
    6. Run a regression analysis
    7. Discuss the findings of the data

@@

Fatigue: The Null hypothesis states that there is no significant difference (p < .05) for the shot accuracy in later periods of the game.

Stress: The Null hypothesis states that there is no significant difference (p < .05) for the shot accuracy in more stressful events.

@@

  1. “Made” and “missed” in “FGM” column were replaced by 1 and 0 respectively.
  2. A new subset was created so that each row contained the player’s name, match details and shooting performance for that player.
  3. The number of attempts and field goal percentage of all players were calculated according to the shooting data. 
  4. The players with most outstanding performances were picked out and another subset was generated for these players.
  5. The correlation (p = .05) between the results of the matches and the performances of top scorers was investigated. 
  6. A logistic regression analysis with the outcome of the match as dependent variable and FGA and percentage of FG made as independent variables was conducted.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```
##Report produced by: Justin Leiendecker, Alexander Romanenko, Artmeis Tomadaki-Balomenou, Zijun Wei, Reza Brianca Widodo  
##Date submitted: 16/10/2016

@@

The NULL Hypothesis: Analysis of means for home and away wins does not show any significant difference in the means.

###Methods
Steps to test the hypothesis are as follows:  
    1. Calculate a total number of games, which has been won by a home or away team
    2. Compare the total win numbers to identify whether home advantage is evident using means of the variables
    3. Extend the analysis to review of the home/away wins on a team level 
    4. Plot the team level data 
    5. Perform a t-test (p .05) to examine whether there is a difference in the means between teams winning at home and teams winning away
    6. Linear regression with "Final margin"" as dependent variable and "Location" as independent variable to examine whether playing at home predicts a higher final margin

Table 1 below shows descriptive statistics for home/away wins:

**Table 1**: Proportion of total games split by Location win factor

@@

@@

The T-test used to verify the differences in the means seen in the plot reached the level of significance, t(58) = -2.39, p = .02.

####Regression analysis

@@

The steps to calculate this measurement are as follows:  
    1. Calculating number of rest days between games for all teams
    3. Calculating ratios for effects of rest days on win/loss form home/away
    4. Perform a Chi-square test to examine whether there is a difference in the distributon for games won and games lost for the different restdays
    5. Calculating ratios for effects of rest days on win/loss form home/away

@@

Fatigue: The Null hypothesis states that there is no significant difference (p < .05) in the mean of shot accuracy in later periods of the game.

Stress: The Null hypothesis states that there is no significant difference (p < .05) in the means for the shot accuracy for lower seconds left on the shot clock.

@@

  1. “Made” and “missed” in “FGM” column were replaced by 1 and 0 respectively.
  2. A new subset was created so that each row contained the player’s name, match details and shooting performance for that player.
  3. The number of attempts and field goal percentage of all players were calculated according to the shooting data. 
  4. The players with most outstanding performances were picked out and another subset was generated for these players.
  5. The correlation (p = .05) between the results of the matches and the performances regarding FGA and FG% of top scorers was investigated. 
  6. A logistic regression analysis with the outcome of the match as dependent variable and FGA and percentage of FG made as independent variables was conducted.
